%-------------------------
% Resume in Latex
% Author : Anirudh Verma
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
    \vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://linkedin.com/in/anirudh-verma-67111514b}{\Large Anirudh Verma}} & Email : \href{mailto:an649hd@gmail.com}{an649hd@gmail.com}\\
  \href{www.linkedin.com/in/anirudh-verma-67111514b}{} & Mobile : \href{tel:+919810410558}{+919810410558} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NIIT University}{Neemrana, Rajasthan}
      {B.Tech in Computer Science; Specialisation Data Science; Minor in Finance;  CGPA: 9.75}{Aug. 2017 -- Jul. 2021}
    \resumeSubheading
      {Amity International School}{Noida, UP}
      {CBSE Board, Class 12 (Senior Secondary) - PCM Percentage: 92.3\%}{}
      {CBSE Board, Class 10 (Secondary) - CGPA: 10}
      % {Bachelor of Engineering in Electrical and Electronics;  GPA: 3.66 (9.15/10.0)}{Aug. 2008 -- July. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bigbasket}{Bangalore, KA}
      {Software Engineer - 2}{Apr 2022 - Present}
      \resumeItemListStart
        \resumeItem{Prime Developer for the WMS Effort - Replenishment}
        {
          \begin{itemize} % Nested list
            \item Developed critical modules for handling replenishment flows in BB2.0, resulting in the gradual elimination of external dependencies.
            \item Estimated recurring cost savings of over $\mathbf{>1.5 crore/month}$ through the project's impact. 
            \item Implemented a high-performance service using low-level aiohttp and aiosql (sqlalchemy), leveraging custom-built abstractions for improved resource utilization and code readability.
            \item Utilized dataclasses and typing extensively to reduce technical debt and improve code maintainability.
            \item Led the migration to Async Django for the UI, resulting in highly responsive UI components with $<1s$ response times, even with complex scenarios involving $>20$ API calls.
            \item Designed and implemented asynchronous consumers capable of processing $12$ Kafka messages simultaneously, reducing the need for scaling up consumers.
            \item Revamped the logging structure, improving indexing and search times for efficient debugging and issue resolution.
            \item Developed a specialized classifier to address validation problems related to replenishment cases around midnight, effectively eliminating instances of double ordering.
            \item Identified and built a new CSRF verification module, enabling the business to maintain a large number of open tabs while preserving the state of each tab.
          \end{itemize}
        }
        \resumeItem{CS Modules}
        {
          \begin{itemize} % Nested list
            \item Optimized response time and expanded the availability of interfaces for CS providers such as Tata and Kapture.
            \item Achieved a significant impact, resulting in cost savings of over $\mathbf{>50 Lakh/month}$
          \end{itemize}
        }
        \resumeItem{Enhancing the base bigbasket asyncio package}
        {
          \begin{itemize} % Nested list
            \item Worked on enhancing the foundational bigbasket asyncio package utilized by Python services.
            \item Implemented improvements to increase performance and efficiency, benefiting the entire system architecture.
          \end{itemize}
        }
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
   \resumeSubSubheading
    {Software Engineer I}{Jul 2021 - Mar 2022}
    \resumeItemListStart
      \resumeItem{Multi-Tenant (First Service in Company) for SaaS spinoff}
      {
        \begin{itemize} % Nested list
          \item Successfully handled the shift of the pilot service (config service) to multi-tenancy, ensuring data isolation without additional infrastructure.
          \item Architected a new implementation addressing observed shortcomings, including an optimized in-memory caching system.
          \item Achieved <10ms response times and ensured coherency across tenants using a revamped zookeeper based synchronisation layer.
          \item Played a critical role in revenue generation from TMS, WMS projects, and SaaS offerings to Croma.
          \item Contributed to building the base multi-tenancy package for Java-based services at Bigbasket.    
        \end{itemize}
      }
      \resumeItem{Integration with Tata Neu}
      {
        \begin{itemize} % Nested list
          \item Developed interfaces for CS integration between Bigbasket and Tata.
          \item Managed daily external client-side interactions as a fresher.
          \item Implemented multi-threaded solutions to enhance throughput and reduce response time for improved CS experience. (from >20s to <0.5s)
        \end{itemize}
      }
      \resumeItem{Added Configuration Hierarchy for EC Group}
      {
        \begin{itemize} % Nested list
          \item Enabled instant and intuitive configuration of services  Pan-India, allowing business-level changes instead of geographical changes.
          \item Example: configuring services for results such as shutting down bb-now or disabling Tata-Neu.
        \end{itemize}
      }
      \resumeItem{Prime developer behind BBNow (Instant-Grocery)}
      {
        \begin{itemize} % Nested list
          \item Designed a new route assignment flow for LMD and implemented a dynamic CEE assignment flow with CEEPool integration.
          \item Solved issues like dirty read and duplicate assignment through optimized assignment procedures.
          \item Developed scripts for data setup and automated testing for BBNow.
          \item Achieved impressive results: 150 successful store launches, 18.7 lakh new orders and 71 Cr. in sales within a 5-month period.
        \end{itemize}
      }
      \resumeItem{Helm Replenishment Service}
      {
        \begin{itemize} % Nested list
          \item Converted the replenishment service to Helm, enabling template-based deployments.
        \end{itemize}
      }
    \resumeItemListEnd
  %  \resumeSubHeadingListEnd

   \resumeSubSubheading
   {Software Engineer Intern}{Jan 2021 - Jun 2021}
   \resumeItemListStart
      \resumeItem{Added SMS Provider}
      {
        \begin{itemize} % Nested list
          \item Revamped bigbasket's SMS system for DLT integration with a new SMS provider.
          \item Implemented a load balancer to enable a switch from a deterministic approach to a probabilistic approach, improving fault tolerance without manual intervention.         
        \end{itemize}
      }
      \resumeItem{Others}
      {CEE Warning System}
    \resumeItemListEnd
  % \resumeSubHeadingListEnd
% -------------------------------------------
    \resumeSubheading
      {Barco}{Noida, UP}
      {Intern}{Jun 2019 - Jul 2019}
      \resumeItemListStart
        \resumeItem{Real Time Dashboard}
        {Developed a Real Time Dashboard that aggregated and visualized all performance metrics from the product line.}
        \resumeItem{Alert System}
        {Built an email alert system that would send a custom scripted email to the appointed manager in case of a system failure.}
        \resumeItem{Reporting System}
        {Created a reporting service that would send reports containing raw and aggreegated data to authorized individuals at set intervals.}
        \resumeItem{Technologies}
        {SQL Server, Node.js, Node-RED, RMM Server, and SSRS}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeItem{Student Counselling Chatbot}
      {
        \begin{itemize} % Nested list
          \item Designed and developed a counselling chatbot solution for a career counselling portal/company.
          \item Successfully deployed the chatbot live in production, providing valuable support to users.
          \item Received recognition as the competition winner among the final 10 participating teams, securing a cash prize of INR 50,000.
          \item Led the project from start to finish, handling functional and technical requirements, creating a comprehensive system design document, and undertaking full-stack development.
          \item Ensured a seamless user experience by focusing on user-friendly features, custom UI design, and support for various devices.
          \item Implemented input flexibility to accommodate different user preferences and enhance the chatbot's usability.
        \end{itemize}
      }
    \resumeItem{Broke Student Brokers}
      {
        \begin{itemize} % Nested list
          \item Built an cross platform android/ios app using Flutter to see portfolio and add funds.
          \item Serverless functions in python created on Google Cloud that would run everyday at 11AM to forecast and perform trades using Alpaca (Simulated), Yahoo Finance and Firebase.
        \end{itemize}
      }
    
    \resumeItem{Smart India Hackathon - 2020}
      {\textbf{'Grand Finalist' (Top $\mathbf{10\%}$)} - ISRO (Indian Space Research Organization).}

  \resumeSubHeadingListEnd

%
% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
    \textbf{Technologies}{: AWS, K8s, Helm, Kafka, GCE, Aerospike, Zookeeper}
    \hfill
    \textbf{Languages}{: Python, Javascript, SQL, Java}

   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
